### 2023-03-25 source/paper/main.tex
General update

\title{College Enrollment and Earnings:
\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Acts}
\author{Ray Huang\thanks{Contact:
    \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback. I would also like to thank Alison Lodermeier and Francesco Ferlenga.}
     \\Brown University, Honors Thesis}

@@

\begin{abstract}
\noindent (aspirational abstract) I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups. The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities. The Fair Sentencing Act of 2010 undid many of these policies. I construct estimates of the impact of these two acts on black males aged 18-24 using three unique counterfactual groups: 1) white males, 2) black females, and 3) black men aged 28-34. I also leverage the variation between high and low drug arrest states. I estimate that the Anti-Drug Act of 1986 resulted in a change in college enrollment rates between XX and XX and a change in earnings between XX and XX. For this subpopulation, this implies estimates of economic returns to education ranging from XX to XX.

@@

\begin{itemize}[itemsep=0.05mm, parsep=0pt]
  \item CPS October supplement
  \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
  \item ACS
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%
a
\clearpage

Note: all figures are limited to ages 18-24 inclusive.

\begin{center}
  \includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_byrace_1986.png}
  \includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_bysex_1986.png}
  \includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_byrace_2010.png}
  \includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_bysex_2010.png}
\end{center}

@@

\begin{center}
  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_byrace_1986.png}
  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_bysex_1986.png}
  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_byrace_2010.png}
  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_bysex_2010.png}
\end{center}

@@

\begin{figure}[h]
  \caption{College enrollment overtime 1986}
  \centering
  \includegraphics[width=1\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}
  \label{fig:TBD}
\end{figure}

@@

\begin{figure}[h]
  \caption{College enrollment overtime 2010}
  \centering
  \includegraphics[width=1\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}
  \label{fig:TBD}
\end{figure}

\begin{figure}[h]
  \caption{Event study 1986, AB arrest rate 18F}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}
  \label{fig:TBD}
\end{figure}

\begin{figure*}[h]
  \caption{Pretrends for Event study 1986, AB arrest rate 18F}
  \includegraphics[width=1\textwidth]{roth_test.png}
\end{figure*}

Power: 0.499. Bayes.Factor: 0.550.  Likelihood.Ratio: 2.024

\begin{figure}[h]
  \caption{Event study 2010, AB arrest rate 18F}
  \centering
  \includegraphics[width=1\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}
  \label{fig:TBD}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%

\import{../../output/tables/summ_stats/}{cps_summ_stats.tex}
\import{../../output/tables/summ_stats/}{ucr_summ_stats.tex}

\import{../../output/tables/}{britton_table2_DiD.tex}
\import{../../output/tables/}{britton_table2_DiD_control_experiment.tex}

\import{../../output/tables/}{britton_table3_DiD.tex}
\import{../../output/tables/}{britton_table3_DiD_control_experiment.tex}

\import{../../output/tables/}{fair_sentencing_DiD_t1.tex}
\import{../../output/tables/}{fair_sentencing_DiD_t1_control_experiment.tex}

\import{../../output/tables/}{fair_sentencing_DiD_t2.tex}
\import{../../output/tables/}{fair_sentencing_DiD_t2_control_experiment.tex}

\import{../../output/tables/}{DiD_1986_high_low.tex}

\import{../../output/tables/}{ddd_1986.tex}

\import{../../output/tables/}{ddiv_show.tex}

>>>>

\title{College Enrollment and Earnings:
\texorpdfstring{\\}{} Examining the Impact of Two Federal Drug Acts}
\author{Ray Huang\thanks{Contact:
    \href{mailto:ray_huang@brown.edu}{ray\_huang@brown.edu}.
     I thank Peter Hull at Brown University for serving as my advisor and for providing me with fantastic feedback. I would also like to thank Alison Lodermeier and Francesco Ferlenga for their guidance and support.}
     \\Brown University, Honors Thesis}

@@

\begin{abstract}
\noindent (to be updated abstract) I examine the impact of two federal drug acts on college enrollments and earnings among black males by using a variety of counterfactual groups. The Anti-Drug Act of 1986 transformed the formerly rehabilitation-focused justice system into a punitive one, imposed sentencing minimums and disparities. The Fair Sentencing Act of 2010 undid many of these policies. I construct estimates of the impact of these two acts on black males aged 18-24 using three unique counterfactual groups: 1) white males, 2) black females, and 3) black men aged 28-34. I also leverage the variation between high and low drug arrest states. I estimate that the Anti-Drug Act of 1986 resulted in a change in college enrollment rates between XX and XX and a change in earnings between XX and XX. For this subpopulation, this implies estimates of economic returns to education ranging from XX to XX.

@@

\begin{itemize}[itemsep=0.05mm, parsep=0pt]
  \item CPS October supplement
  \begin{itemize}
    \item Dropped observations with missing family income data
    \item Edtype is the variable used for college enrollment, 
  \end{itemize}
  \item UCR from ICPSR (missing data problem, many counties failed to report arrest rates for the relevant crimes)
  \begin{itemize}
    \item Arrest data normalized per 100000. State population data are based on U.S. Census Bureau midyear population estimates.
  \end{itemize}
  \item ACS
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%FIGURES%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\input{figures.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%TABLES%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tables.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%APPENDIX%%%%%%%%%%%%%%%%%%%%%%%%%%%
